Open Preprints in Ecology \& Evolution

### 2012-09-05 ms.tex
Basic sketch
A basic sketch of my section on arXiv.  The ideas that I want to present
are all there, but the wording needs working.

@@

\section{Current offer}

@@

arXiv (\href{http://arxiv.org/}{http://arxiv.org/}).
arXiv is funded by a network of universities.

% @Joel

>>>>

\author{Joel J. Adamson}
\affiliation{Ecology, Evolution and Organismic Biology, University of North Carolina at Chapel Hill}

@@

\section{Current offerings}

@@

% @Joel
% Rough outline:
% 1. Description of arXiv (origins, funding, maintenance)
% 2. Submission process
% 3. Role within math and physics community (nearly universal), including recent changes
% 4. Nature of citations and "priority"
%
% My biggest problem here is how to cite my sources: the information
% on funding comes from a press release from Cornell University
% Libraries; other basic "raw data" comes straight from the arXiv
% webpages. How do I cite that?

arXiv (\href{http://arxiv.org/}{http://arxiv.org/}) is the most
widely-used preprint server available today, and its use is almost
universal in mathematics and most branches of physics.  arXiv receives
over 7,000 submissions per month
(http://arxiv.org/show_monthly_submissions).  Paul Ginsparg originated
ArXiv for high-energy physicists to communicate preprints via email
and ftp.  Soon after its origination the world-wide web became
available.

Submission to arXiv is fully automated via the world-wide web.
Authors can submit LaTeX documents or directly in PDF format.  A
moderation system was put in place in 2004: papers must be categorized
by a moderator.  At least one author of a paper must be an
``endorser'' that has previously submitted a paper or has received
permission to submit.  Endorser status is automatic for members of
recognized academic institutions.

Most papers posted to arXiv are eventually printed in journals.  There
are notable exceptions, including Perelman's landmark paper solving
the Poincar\'{e} conjecture \cite{2002math.....11159P}.

arXiv is now administered by the Cornell University Libraries.
Funding comes from voluntary pledges by academic institutions along
with matching funds from the Simons Foundation \cite{arxiv_future}.
One-hundred twenty six of the top two-hundred institutions in terms of
downloads have provided the operating budget for arXiv over the next
five years.  This plan reduces the financial burden on Cornell
University and transfers governance to a collaborative community in
accordance with arXiv's key principles.
